The 300 km~s$^{-1}$ stellar stream near Segue\,1: Insights From High-Resolution Spectroscopy of its brightest star

### 2012-08-16 2012-segue-1/segue_draft2.tex
added 2012 segue 1 paper + data. This is the pre-draft before it was re-sent out to the co-authors

\documentclass[manuscript]{aastex}
%\documentclass[11pt,preprint]{aastex}
%% preprint2 produces a double-column, single-spaced document:
%\documentclass{emulateapj}
%\documentclass[preprint2]{aastex}

@@

\begin{abstract}
In kinematic surveys of the faint satellite galaxy Segue\,1, an overdensity of stars with velocities around 300~km~s$^{-1}$ has been seen, first seen in \citet{Geha2009} and interpreted as a possible stellar stream. We present a high-resolution spectrum and abundance analysis of Segue1-11, the brightest likely stream member star from the kinematic sample of \citet{Norris2010a}. We determine a metallicity of [Fe/H] $ = -1.44$ for Segue1-11, and find abundance patterns similar to typical halo stars at this metallicity. Comparing our stellar parameter solution to theoretical isochrones, we estimate a distance of $18 \pm 7$ kpc. Both the metallicity and distance estimates are in good agreement with what can be inferred from comparing the SDSS photometric data of the stream stars to globular cluster sequences. While several other structures overlap with the stream in this part of the sky, the combination of kinematic, chemical and distance information makes it unlikely that these stars are associated with either the Segue\,1 galaxy, the Sagittarius stream or the Orphan stream.

@@

In the $\Lambda$CDM model, structure builds up hierarchically, with smaller objects merging to build larger ones. One consequence of this is stellar streams in the galactic halo, produced as accreted objects are tidally disrupted (see e.g. \citealt{Lynden-Bell1995} and references therein). A well-known example is the stream extending from the Sagittarius dwarf spheroidal, which has been traced more than one full wrap around the Milky Way \citep[e.g.][]{Ibata1994, Majewski2003}. In a particularly busy piece of sky dubbed the ``Field of Streams'' \citep{Belokurov2006b}, at least two wraps of the Sagittarius stream as well as several other structures are visible.

@@

There are two existing medium-resolution spectroscopic studies of the region around Segue\,1, N10 and S11. N10's data was obtained with the Anglo-Australian Telescope's AAOmega spectrograph, which can take simultaneous spectra of 400 targets over a field 2$^{\circ}$ in diameter. They were targeting stars in the RGB locus. S11, on the other hand, were using the {\small DEIMOS} spectrograph on the KeckII telescope, focusing on an area within $\sim 15$\arcmin of the center of Segue\,1, and going deeper than N10. Table~\ref{tab:members} lists all stars (52 total) in the two samples with heliocentric radial velocities higher than 240~km~s$^{-1}$, i.e. stars with higher velocities than consistent with Segue\,1 membership and so potential stream candidates. This includes four targets from the AAOmega sample not published in N10 due to slightly lower confidence in the radial velocity measurement.

Figure~\ref{fig:col_mag} summarizes the properties of the two samples. The top left panel shows a histogram of the heliocentric radial velocities measured. The central peak ($\sim$ 270-330~km~s$^{-1}$) has a mean velocity of 300~km~s$^{-1}$ and a dispersion of 10.3~km~s$^{-1}$. Considering the independent N10 and S11 samples separately we still arrive at a dispersion of 10~km~s$^{-1}$ for the central peak, and similar means (303~km~s$^{-1}$ for N10 versus 298~km~s$^{-1}$ for S11). It is not clear whether the intermediate ``bridge'' candidates with 240~km~s$^{-1}$ $< v_{helio} < $270~km~s~$^{-1}$ or the three extreme-velocity stars with $v_{helio} > $ 340~km~s$^{-1}$ should be considered part of the same structure, but follow-up observations tracing the stream over a larger field of view could resolve this. Either way, the mean velocity of this structure is extreme, and the dispersion is resolved and high -- it is not a cold stream.

The top right panel of Fig.~\ref{fig:col_mag} shows the color-magnitude diagram of all the stream candidate stars from Table~\ref{tab:members}. Here, stream candidates are shown as black circles. (Three stars redder than $(g-i) = 1.2 $ are not shown.) For comparison, the green triangles show radial velocity members of the Segue\,1 dwarf galaxy, which was the target of the N10 and S11 studies. Open symbols show stars from the N10/AAO sample, while filled symbols are from the S11 sample. Note that the N10 sample covers a much larger field of view but does not go as deep -- as a result, most of the bright stream stars, including our target (star symbol), show up in this sample. In order to illustrate the photometric criteria used in the samples, the blue and red dots show the stars observed by N10 and S11, respectively, that meet their photometric selection cut but are radial velocity non-members of Segue\,1 and the stream.

The solid line shows the M5 cluster sequence \citep{An2008}, which gives a good fit to the stream main sequence and subgiant branch when shifted to a distance of 18~kpc. The metallicity of M5 is [Fe/H] $= -1.3$, and so the SDSS photometry suggests that the stream is slightly more metal-rich than Segue\,1. The red giant branch of the stream is bluer than this sequence, however, and is better fit by e.g. the RGB of the more metal-poor cluster M92.

@@

\begin{table}
 \begin{threeparttable}
  \begin{center}
    \caption{Stream Member Candidate Stars}
    \label{tab:members}
    {\tiny
    \begin{tabular}{c c c c c c}
     \hline \hline

       Identifier                    & $g$     &  $r$    &    $i$    & $v_{hel}$ & Ref.       \\ \hline  
     SDSSJ100914.95+155948.4\tnote{a}     & 17.997   & 17.495   & 17.262     &  307  & N10     \\
     SDSSJ100740.13+160309.7\tnote{b}    & 19.965   & 19.551   & 19.448     &  298	& N10     \\
     SDSSJ100659.01+154418.8         & 19.721   & 19.333   & 19.144     &  307	& N10     \\ 
     SDSSJ100651.80+154941.5         & 20.365   & 20.049   & 19.911     &  300 	& AAO     \\
     SDSSJ100619.95+154612.7         & 20.094   & 19.786   & 19.679     &  315 	& AAO     \\
     SDSSJ100612.02+154548.4         & 20.080   & 19.626   & 19.616     &  327	& N10     \\
     SDSSJ100530.59+155418.1         & 19.831   & 19.493   & 19.314     &  305	& N10     \\
     SDSSJ100627.73+155408.6         & 20.155   & 19.880   & 19.711     &  300	& AAO     \\
     SDSSJ100647.74+161330.1         & 20.011   & 19.704   & 19.516     &  300  & AAO     \\
     SDSSJ100658.49+162045.6         & 19.840   & 19.379   & 19.187     &  295	& N10     \\
     SDSSJ100839.66+162826.7         & 19.169   & 18.739   & 18.608     &  288	& N10     \\   
     SDSSJ100600.16+160518.6         & 20.220	& 19.688   & 19.518	&  242  & N10     \\
     SDSSJ100618.74+160339.0         & 21.678   & 21.147   & 20.906     &  268  & S11     \\
     SDSSJ100619.99+160042.1         & 21.705   & 21.417   & 21.180     &  305	& S11     \\
     SDSSJ100630.89+161512.1         & 21.479   & 21.131   & 20.952     &  321	& S11     \\
     SDSSJ100642.76+155709.3         & 21.562   & 21.233   & 21.029     &  291	& S11     \\
     SDSSJ100646.78+160608.3         & 20.534   & 20.221   & 20.076     &  294	& S11     \\
     SDSSJ100648.52+160958.1         & 20.279   & 19.980   & 19.798     &  306	& S11     \\
     SDSSJ100650.83+160351.2         & 22.137   & 21.952   & 21.838     &  312	& S11     \\
     SDSSJ100654.23+155520.7         & 22.127   & 21.533   & 21.290     &  268	& S11     \\
     SDSSJ100656.13+160660.0         & 21.347   & 21.099   & 20.994     &  302	& S11     \\
     SDSSJ100658.54+155748.9         & 21.562   & 21.096   & 20.840     &  290	& S11     \\
     SDSSJ100704.58+160130.8         & 21.229   & 20.814   & 20.762     &  295	& S11     \\
     SDSSJ100704.63+160812.6         & 21.088   & 20.851   & 20.743     &  296	& S11     \\
     SDSSJ100708.37+155646.3         & 22.039   & 21.562   & 21.458     &  286	& S11     \\
     SDSSJ100709.07+160436.6         & 22.292   & 21.889   & 21.576     &  312	& S11     \\
     SDSSJ100709.74+155312.3         & 16.113   & 15.833   & 15.721     &  303	& S11     \\
     SDSSJ100712.96+155734.8         & 18.287   & 18.009   & 17.872     &  307	& S11     \\
     SDSSJ100713.69+160444.8         & 22.139   & 21.765   & 21.476     &  293	& S11     \\
     SDSSJ100715.51+160552.1         & 20.360   & 20.076   & 19.974     &  282	& S11     \\
     SDSSJ100715.53+161519.1         & 20.741   & 20.439   & 20.427     &  266	& S11     \\
     SDSSJ100717.15+160511.9         & 22.104   & 21.781   & 21.385     &  266	& S11     \\
     SDSSJ100717.36+160355.6         & 20.116   & 19.778   & 19.646     &  295	& S11     \\
     SDSSJ100720.00+160137.5         & 17.626   & 17.274   & 17.127     &  312	& S11     \\
     SDSSJ100721.16+161118.2         & 20.990   & 19.732   & 19.203     &  281	& S11     \\
     SDSSJ100721.77+155424.5         & 20.619   & 20.223   & 20.220     &  307	& S11     \\
     SDSSJ100729.58+161107.1         & 20.358   & 19.347   & 19.026     &  309  & S11     \\     
     SDSSJ100732.47+160500.5         & 22.588   & 22.043   & 21.911     &  281	& S11     \\
     SDSSJ100734.97+155431.5         & 20.788   & 20.542   & 20.391     &  303	& S11     \\
     SDSSJ100737.37+160746.2         & 21.253   & 20.992   & 20.812     &  296	& S11     \\
     SDSSJ100740.15+155855.6         & 21.323   & 20.969   & 20.809     &  295	& S11     \\
     SDSSJ100742.51+160006.8         & 22.476   & 22.024   & 21.463     &  296	& S11     \\
     SDSSJ100743.78+154932.9         & 22.472   & 20.985   & 20.369     &  299	& S11     \\
     SDSSJ100747.19+160545.5         & 20.135   & 19.770   & 19.677     &  294	& S11     \\ 
     SDSSJ100735.92+161125.7         & 23.791   & 22.084   & 22.003    &  242  & S11     \\
     SDSSJ100625.70+155422.1         & 21.587   & 21.135   & 20.950    &  244	& S11     \\
     SDSSJ100711.80+160630.4         & 22.802   & 22.160   & 21.952    &  247	& S11     \\
     SDSSJ100707.80+160721.5         & 20.643   & 20.342   & 20.239    &  248	& S11     \\
     SDSSJ100735.24+155715.3         & 22.535   & 21.135   & 20.411    &  255	& S11     \\
     SDSSJ100628.41+155628.8         & 17.852   & 17.560   & 17.431    &  347	& S11     \\
     SDSSJ100736.92+155958.9         & 21.994   & 21.871   & 21.609    &  373	& S11     \\
     SDSSJ100651.74+161759.2         & 21.407   & 20.923   & 20.953    &  394	& S11     \\ \hline

     \end{tabular} }
     \begin{tablenotes}
       \item[a]{{\tiny Segue1-11, target star.}}
%       \item[b]{{\tiny From high-resolution measurement (this paper).}}
       \item[b]{{\tiny Observed by both N10 and S11.}}
      \end{tablenotes}
     \end{center}
   \end{threeparttable}
\end{table}

@@

\begin{table}
 \begin{threeparttable}
 \begin{center}
   \caption{Targets: Segue1-11 and comparison stars}
   \label{tab:targets}
   \begin{tabular}{l c c c c}
     \hline \hline
       Name       &  RA            & Dec             & V$_{\mbox{mag}}$ & B-V       \\ \hline  
       Segue 1-11 &  $10:09:14.95$ &  $+15:59:48.4$  & 17.70\tnote{a}   &  0.68\tnote{a}       \\
       HIP37335   &  $07:39:50.11$ &  $-01:31:20.37$ & 9.25             &  0.82       \\
       HIP47139   &  $09:36:19.95$ &  $-20:53:14.75$ & 8.34             &  1.01       \\
       HIP68807   &  $14:05:13.02$ &  $-14:51:25.45$ & 7.25             &  0.93       \\ \hline    
  \end{tabular}
  \begin{tablenotes}
   \item[a]{Transformed from the SDSS photometry following \citet{Jordi2006}}
  \end{tablenotes}
 \end{center}
\end{threeparttable}
\end{table}

\begin{table}
 \begin{center}
   \caption{Summary of Observations}
   \label{tab:segobs}
   \begin{tabular}{c c c c }
     \hline \hline
       Object    &  UT date    & UT start time & t$_{\mbox{exp}}$ (s)   \\ \hline  
       Segue1-11 &  03/08/2010 & 02:35         & 3000            \\
       Segue1-11 &  03/08/2010 & 05:30         & 3600            \\
       Segue1-11 &  03/19/2010 & 05:06         & 3000            \\
       Segue1-11 &  03/22/2010 & 00:37         & 3100            \\
       Segue1-11 &  03/22/2010 & 05:22         & 2800            \\
       Segue1-11 &  03/23/2010 & 05:08         & 700             \\
       HIP37335  &  03/13/2011 & 23:41         &  7              \\
       HIP68807  &  03/12/2011 & 10:08         &  1              \\
       HIP47139  &  03/13/2011 & 23:53         &  5              \\
      \hline
  \end{tabular}
 \end{center}
\end{table}

\begin{figure}
 \begin{center}
  \includegraphics[width=9cm]{Mgspecs.ps}
  \caption{High-resolution spectrum of our target star, Segue1-11, and the three comparison stars from the F00 sample, in the region around the Mg b-lines. Shown here are the short exposures of the comparison stars, taken to obtain a similar resolution and S/N as the Segue1-11 spectrum.}
  \label{fig:mglines}
 \end{center}
\end{figure}

\subsection{Line Strength Measurements}
\label{sec:linemes}
We obtained a first estimate for the radial velocity from the two strong Mg b lines in the green region of the spectrum, and two additional Mg lines in the blue. Equivalent widths were then measured by fitting Gaussian profiles, and our estimate corrected based on the mean radial velocity from all the lines measured. Using these 366 lines, we find a heliocentric radial velocity of $307.62$~km~s$^{-1}$, with a standard error of the mean of 0.09~km~s$^{-1}$. This is slightly higher than the estimate of $301$~km~s$^{-1}$ from N10 based on the medium resolution spectrum, but consistent within their estimated velocity uncertainty of 10~km~s$^{-1}$. We note that our measurement is well within the estimated range for the 300~km~s$^{-1}$ stream.

@@

For comparison, we also use the SDSS colors to determine the temperature photometrically by interpolating the SDSS {\it ugriz} colors to the isochrones from \citet{Kim2002}, using the color tables of Castelli (http://wwwuser.oat.ts.astro.it/castelli/).  This results in a slightly warmer solution (depending on which colors we use), with T$_{\mbox{\small{eff}}} \sim 5400$ K and $\log g \sim 3.5$. If we instead use this set of stellar parameters, we would arrive at [Fe/H] of $-1.3$. This is, however, well within our estimate of uncertainty for the metallicity (see Section~\ref{sec:unc}). For the rest of the analysis, we use the parameters derived from spectroscopy, however, to facilitate comparison with the Fulbright/Hipparcos stars.

\begin{table}
\begin{threeparttable}
 \begin{center}
   \caption{Stellar parameters: Segue1-11 and comparison stars}
   \label{tab:comp_para}
   \begin{tabular}{l c c c c  }
     \hline \hline
       Name       &  T$_{\mbox{\tiny{eff}}}$ (K) & $\log$ g  & [Fe/H]            & $v_{\mu}$ (km~s$^{-1}$)   \\ \hline  
       Segue 1-11 &  5200          &  2.6      & $-1.4$            & 1.5                \\
       HIP37335\tnote{a}   &  5100 (4850)   &  2.9 (2.7)& $-1.0$ ($-1.2$)   & 1.5 (1.5)           \\
       HIP47139   &  4550 (4600)   &  0.9 (1.3)& $-1.6$ ($-1.4$)   & 2.3 (1.8)          \\
       HIP68807   &  4600 (4575)   &  1.0 (1.1)& $-1.8$ ($-1.8$)   & 2.0 (1.9)          \\ \hline
  \end{tabular}
  \begin{tablenotes}
  \item[a]{While our solution for HIP37335 is warmer than what was found in F00, we note that our solution agrees with other literature sources for this star \citep[e.g.,][]{Soubiran2008, Cenarro2007, Peterson1981}.}
  \end{tablenotes}
 \end{center}
 \end{threeparttable}
\end{table}

@@

>>>>

\documentclass{emulateapj}
%\documentclass[11pt,preprint]{aastex}
%% preprint2 produces a double-column, single-spaced document:
%\documentclass{emulateapj}
%\documentclass[preprint2]{aastex}

@@

\begin{abstract}
In kinematic surveys of the faint satellite galaxy Segue\,1, an overdensity of stars with velocities around 300~km~s$^{-1}$ has been seen, first seen in \citet{Geha2009} and interpreted as a possible stellar stream. We present a high-resolution spectrum and abundance analysis of Segue1-11, the brightest likely stream member star from the kinematic sample of \citet{Norris2010a}. We determine a metallicity of [Fe/H] $ = -1.44 \pm XX$ for Segue1-11, and find abundance patterns similar to typical halo stars at this metallicity. Comparing our stellar parameter solution to theoretical isochrones, we estimate a distance of $18 \pm 7$ kpc. Both the metallicity and distance estimates are in good agreement with what can be inferred from comparing the SDSS photometric data of the stream stars to globular cluster sequences. While several other structures overlap with the stream in this part of the sky, the combination of kinematic, chemical and distance information makes it unlikely that these stars are associated with either the Segue\,1 galaxy, the Sagittarius stream or the Orphan stream.

@@

In the $\Lambda$CDM model, structure builds up hierarchically, with smaller objects merging to build larger ones. One consequence of this is stellar streams in the galactic halo, produced as accreted objects are tidally disrupted (see e.g. \citealt{Lynden-Bell1995} and references therein). A well-known example is the stream extending from the Sagittarius dwarf spheroidal, which has been traced more than one full wrap around the Milky Way \citep[e.g.][]{Ibata1994, Majewski2003}. In a part of the sky dubbed the ``Field of Streams'' \citep{Belokurov2006b}, at least two wraps of the Sagittarius stream as well as several other structures are visible.

@@

There are two existing medium-resolution spectroscopic studies of the region around Segue\,1, N10 and S11. N10's data was obtained with the Anglo-Australian Telescope's AAOmega spectrograph, which can take simultaneous spectra of 400 targets over a field 2$^{\circ}$ in diameter. They were targeting stars in the RGB locus. S11, on the other hand, were using the {\small DEIMOS} spectrograph on the KeckII telescope, focusing on an area within $\sim 15$\arcmin of the center of Segue\,1, and going deeper than N10. Table~\ref{tab:members} lists all stars (52 total) in the two samples with heliocentric radial velocities higher than 240~km~s$^{-1}$, i.e. stars with higher velocities than consistent with Segue\,1 membership and so potential stream candidates. This includes four targets from the AAOmega sample not published in N10 due to slightly lower confidence in the radial velocity measurement. All photometry is from the Sloan Digital Sky Survey, DR7 \citep{Abazajian2009}. The estimated velocity uncertainty for the N10 stars is 10~km~s$^{-1}$; the individual velocity uncertainties for S11 stars are shown in the table.

Figure~\ref{fig:col_mag} summarizes the properties of the two samples. The top left panel shows a histogram of the heliocentric radial velocities measured. The central peak ($\sim$ 270-330~km~s$^{-1}$) has a mean velocity of $300.4 \pm 1.1 \mbox{km s}^{-1}$ and a dispersion of $10.3 \pm 1.2 \mbox{km s}^{-1}$. Considering the independent N10 and S11 samples separately we still arrive at a dispersion of 10~km~s$^{-1}$ for the central peak, and similar means ($303.3 \pm 3$~km~s$^{-1}$ for N10 versus $299.1 \pm 1$~km~s$^{-1}$ for S11). It is not clear whether the intermediate ``bridge'' candidates with 240~km~s$^{-1}$ $< v_{helio} < $270~km~s~$^{-1}$ or the three extreme-velocity stars with $v_{helio} > $ 340~km~s$^{-1}$ should be considered part of the same structure, but follow-up observations tracing the stream over a larger field of view could resolve this. Either way, the mean velocity of this structure is extreme, and the dispersion is resolved and high -- it is not a cold stream.

The top right panel of Fig.~\ref{fig:col_mag} shows the color-magnitude diagram of all the stream candidate stars from Table~\ref{tab:members}. Here, stream candidates are shown as black circles. (Three stars redder than $(g-i) = 1.2 $ are not shown.) For comparison, the green triangles show radial velocity members of the Segue\,1 dwarf galaxy, which was the target of the N10 and S11 studies. Open symbols show stars from the N10/AAO sample, while filled symbols are from the S11 sample. Note that the N10 sample covers a much larger field of view but does not go as deep -- as a result, most of the bright stream stars, including our target (star symbol), show up in this sample. In order to illustrate the photometric criteria used in the samples, the blue and red dots show the stars observed by N10 and S11, respectively, that met their photometric selection cut for follow-up spectroscopy, but are radial velocity non-members of Segue\,1 and the stream.

The solid line shows the M5 cluster sequence \citep{An2008}, which gives a good fit to the stream main sequence and subgiant branch when shifted to a distance of 18~kpc. The metallicity of M5 is [Fe/H] $= -1.3$, and the SDSS photometry suggests that the stream is slightly more metal-rich than Segue\,1 \citep{Simon2011}. The red giant branch of the stream is bluer than this sequence, however, and is better fit by e.g. the RGB of the more metal-poor cluster M92.

@@

\begin{deluxetable*}{lcccccccc}
\tabletypesize{\scriptsize}
\tablecaption{Stream Member Candidate Stars\label{tab:members}}
\tablehead{
	\colhead{Identifier} &
	\colhead{R. A.} &
	\colhead{Dec.} &
	\colhead{$g$} &
	\colhead{$r$} &
	\colhead{$i$} &
	\colhead{$g \-- r$} &
	\colhead{$V_{hel}$} &
	\colhead{Ref} \\
  & (J2000) & (J2000) & & & & & (km s$^{-1}$) &  
}
\startdata
300S-1\tablenotemark{a} & 10\phn09\phn15.0 & $+$15\phn59\phn48.4 &  17.99 & 17.49 & 17.26 & 0.73 & 307 & N10 \\
300S-2 & 10\phn07\phn40.1 & $+$16\phn03\phn09.7 &  19.96 & 19.55 & 19.44 & 0.52 & 298 & N10, S11    \\
300S-3 & 10\phn06\phn59.0 & $+$15\phn44\phn18.8 &  19.72 & 19.33 & 19.14 & 0.58 & 307 & N10     \\
300S-4 & 10\phn06\phn51.8 & $+$15\phn49\phn41.5 &  20.36 & 20.04 & 19.91 & 0.45 & 300 & AAO     \\
300S-5 & 10\phn06\phn20.0 & $+$15\phn46\phn12.7 &  20.09 & 19.78 & 19.67 & 0.42 & 315 & AAO     \\
300S-6 & 10\phn06\phn12.0 & $+$15\phn45\phn48.4 &  20.08 & 19.62 & 19.61 & 0.47 & 327 & N10     \\
300S-7 & 10\phn05\phn30.6 & $+$15\phn54\phn18.1 &  19.83 & 19.49 & 19.31 & 0.52 & 305 & N10     \\
300S-8 & 10\phn06\phn27.7 & $+$15\phn54\phn08.6 &  20.15 & 19.88 & 19.71 & 0.44 & 300 & AAO     \\
300S-9 & 10\phn06\phn47.7 & $+$16\phn13\phn30.1 &  20.01 & 19.70 & 19.51 & 0.50 & 300 & AAO     \\
300S-10 & 10\phn06\phn58.5 & $+$16\phn20\phn45.6 &  19.84 & 19.37 & 19.18 & 0.66 & 295 & N10     \\
300S-11 & 10\phn08\phn39.7 & $+$16\phn28\phn26.7 &  19.16 & 18.73 & 18.60 & 0.56 & 288 & N10     \\
300S-12 & 10\phn06\phn00.2 & $+$16\phn05\phn18.6 &  20.22 & 19.68 & 19.51 & 0.71 & 242 & N10      \\
300S-13 & 10\phn06\phn18.7 & $+$16\phn03\phn39.0 &  21.67 & 21.14 & 20.90 & 0.77 & 268.6  $\pm$\phn3.1 & S11     \\
300S-14 & 10\phn06\phn20.0 & $+$16\phn00\phn42.1 &  21.70 & 21.41 & 21.18 & 0.52 & 305.5  $\pm$\phn4.3 & S11     \\
300S-15 & 10\phn06\phn30.9 & $+$16\phn15\phn12.1 &  21.47 & 21.13 & 20.95 & 0.52 & 321.0  $\pm$\phn8.8 & S11     \\
300S-16 & 10\phn06\phn42.8 & $+$15\phn57\phn09.3 &  21.56 & 21.23 & 21.02 & 0.54 & 291.9  $\pm$\phn6.4 & S11     \\
300S-17 & 10\phn06\phn46.8 & $+$16\phn06\phn08.3 &  20.53 & 20.22 & 20.07 & 0.46 & 294.5  $\pm$\phn2.9 & S11     \\
300S-18 & 10\phn06\phn48.5 & $+$16\phn09\phn58.1 &  20.27 & 19.98 & 19.79 & 0.48 & 306.0  $\pm$\phn2.6 & S11     \\
300S-19 & 10\phn06\phn50.8 & $+$16\phn03\phn51.2 &  22.13 & 21.95 & 21.83 & 0.30 & 312.6  $\pm$11.9 & G09, S11     \\
300S-20 & 10\phn06\phn54.2 & $+$15\phn55\phn20.7 &  22.12 & 21.53 & 21.29 & 0.83 & 268.5  $\pm$\phn6.2 & S11     \\
300S-21 & 10\phn06\phn56.1 & $+$16\phn06\phn60.0 &  21.34 & 21.09 & 20.99 & 0.35 & 302.0  $\pm$\phn2.6 & S11     \\
300S-22 & 10\phn06\phn58.5 & $+$15\phn57\phn48.9 &  21.56 & 21.09 & 20.84 & 0.72 & 290.5  $\pm$\phn3.6 & S11     \\
300S-23 & 10\phn07\phn04.6 & $+$16\phn01\phn30.8 &  21.22 & 20.81 & 20.76 & 0.46 & 295.8  $\pm$\phn3.9 & S11     \\
300S-24 & 10\phn07\phn04.6 & $+$16\phn08\phn12.6 &  21.08 & 20.85 & 20.74 & 0.34 & 296.9  $\pm$\phn3.4 & S11     \\
300S-25 & 10\phn07\phn08.4 & $+$15\phn56\phn46.3 &  22.03 & 21.56 & 21.45 & 0.58 & 286.3  $\pm$\phn5.4 & S11     \\
300S-26 & 10\phn07\phn09.1 & $+$16\phn04\phn36.6 &  22.29 & 21.88 & 21.57 & 0.72 & 312.7  $\pm$\phn6.4 & S11     \\
300S-27 & 10\phn07\phn09.7 & $+$15\phn53\phn12.3 &  16.11 & 15.83 & 15.72 & 0.39 & 303.4  $\pm$\phn2.2 & S11     \\
300S-28 & 10\phn07\phn13.0 & $+$15\phn57\phn34.8 &  18.28 & 18.00 & 17.87 & 0.41 & 307.9  $\pm$\phn2.4 & S11     \\
300S-29 & 10\phn07\phn13.7 & $+$16\phn04\phn44.8 &  22.13 & 21.76 & 21.47 & 0.66 & 293.4  $\pm$\phn4.8 & G09, S11     \\
300S-30 & 10\phn07\phn15.5 & $+$16\phn05\phn52.1 &  20.36 & 20.07 & 19.97 & 0.39 & 282.0  $\pm$\phn2.8 & S11     \\
300S-31 & 10\phn07\phn15.5 & $+$16\phn15\phn19.1 &  20.74 & 20.43 & 20.42 & 0.32 & 266.8  $\pm$\phn3.1 & S11     \\
300S-32 & 10\phn07\phn17.2 & $+$16\phn05\phn11.9 &  22.10 & 21.78 & 21.38 & 0.72 & 266.3  $\pm$\phn4.4 & S11     \\
300S-33 & 10\phn07\phn17.4 & $+$16\phn03\phn55.6 &  20.11 & 19.77 & 19.64 & 0.47 & 295.9  $\pm$\phn2.4 & G09, S11    \\
300S-34 & 10\phn07\phn20.0 & $+$16\phn01\phn37.5 &  17.62 & 17.27 & 17.12 & 0.50 & 312.7  $\pm$\phn2.2 & S11     \\
300S-35 & 10\phn07\phn21.2 & $+$16\phn11\phn18.2 &  20.99 & 19.73 & 19.20 & 1.79 & 281.6  $\pm$\phn2.4 & S11     \\
300S-36 & 10\phn07\phn21.8 & $+$15\phn54\phn24.5 &  20.61 & 20.22 & 20.22 & 0.39 & 307.2  $\pm$\phn5.5 & S11     \\
300S-37 & 10\phn07\phn29.6 & $+$16\phn11\phn07.1 &  20.35 & 19.34 & 19.02 & 1.33 & 309.6  $\pm$\phn2.2 & S11     \\
300S-38 & 10\phn07\phn32.5 & $+$16\phn05\phn00.5 &  22.58 & 22.04 & 21.91 & 0.67 & 281.1  $\pm$\phn6.9 & G09, S11     \\
300S-39 & 10\phn07\phn35.0 & $+$15\phn54\phn31.5 &  20.78 & 20.54 & 20.39 & 0.39 & 303.2  $\pm$\phn2.8 & S11     \\
300S-40 & 10\phn07\phn37.3 & $+$16\phn07\phn46.2 &  21.25 & 20.99 & 20.81 & 0.44 & 296.0  $\pm$\phn3.9 & S11     \\
300S-41 & 10\phn07\phn40.2 & $+$15\phn58\phn55.6 &  21.32 & 20.96 & 20.80 & 0.52 & 295.8  $\pm$\phn3.8 & S11     \\
300S-42 & 10\phn07\phn42.5 & $+$16\phn00\phn06.8 &  22.47 & 22.02 & 21.46 & 1.01 & 296.6  $\pm$10.3 & S11     \\
300S-43 & 10\phn07\phn43.8 & $+$15\phn49\phn32.9 &  22.47 & 20.98 & 20.36 & 2.11 & 299.2  $\pm$\phn2.5 & S11     \\
300S-44 & 10\phn07\phn47.2 & $+$16\phn05\phn45.5 &  20.13 & 19.77 & 19.67 & 0.46 & 294.3  $\pm$\phn2.4 & S11     \\
300S-45 & 10\phn07\phn35.9 & $+$16\phn11\phn25.7 &  23.79 & 22.08 & 22.00 & 1.79 & 242.2  $\pm$\phn7.8 & S11     \\
300S-46 & 10\phn06\phn25.7 & $+$15\phn54\phn22.1 &  21.58 & 21.13 & 20.95 & 0.63 & 244.3  $\pm$\phn5.6 & S11     \\
300S-47 & 10\phn07\phn11.8 & $+$16\phn06\phn30.4 &  22.80 & 22.16 & 21.95 & 0.85 & 247.1  $\pm$15.9 & S11     \\
300S-48 & 10\phn07\phn07.8 & $+$16\phn07\phn21.5 &  20.64 & 20.34 & 20.23 & 0.41 & 247.7  $\pm$\phn2.8 & S11     \\
300S-49 & 10\phn07\phn35.2 & $+$15\phn57\phn15.3 &  22.53 & 21.13 & 20.41 & 2.12 & 255.1  $\pm$\phn3.0 & S11     \\
300S-50 & 10\phn06\phn28.4 & $+$15\phn56\phn28.8 &  17.85 & 17.56 & 17.43 & 0.42 & 347.1  $\pm$\phn2.9 & S11     \\
300S-51 & 10\phn07\phn36.9 & $+$15\phn59\phn58.9 &  21.99 & 21.87 & 21.60 & 0.39 & 373.0  $\pm$\phn6.0 & S11     \\
300S-52 & 10\phn06\phn51.7 & $+$16\phn17\phn59.2 &  21.40 & 20.92 & 20.95 & 0.45 & 394.9  $\pm$\phn8.9 & S11 
\enddata
\tablenotetext{a}{Target star, referenced as Segue1-11 in N10}
\end{deluxetable*}

@@

\begin{deluxetable*}{lcccccccc}
\tabletypesize{\scriptsize}
\tablecaption{Observed Targets \label{tab:targets}}
\tablehead{
	\colhead{Name} &
	\colhead{R. A.} &
	\colhead{Dec.} &
	\colhead{$V$} &
	\colhead{$B \-- V$} & 
	\colhead{UT Date} &
	\colhead{UT Start} &
	\colhead{$t_{exp}$} \\
  & (J2000) & (J2000) & & & & & ($s$)   
}
\startdata  
300S-1     &  10\phn09\phn15.0 &  $+$15\phn59\phn48.4 & 17.70\tablenotemark{a} &  0.68\tablenotemark{a} & 03/08/2010 & 02:35 & 3000 \\
 & & & & & 03/08/2010 & 05:30 & 3600 \\
 & & & & & 03/19/2010 & 05:06 & 3000 \\
 & & & & & 03/22/2010 & 00:37 & 3100 \\
 & & & & & 03/22/2010 & 05:22 & 2800 \\
 & & & & & 03/23/2010 & 05:08 & 700 \\
HIP37335   &  07\phn39\phn50.1 &  $-$01\phn31\phn20.4 & 9.25 &  0.82 & 03/13/2011 & 23:41 & 7      \\
HIP47139   &  09\phn36\phn20.0 &  $-$20\phn53\phn14.8 & 8.34 &  1.01 & 03/12/2011 & 10:08 & 1      \\
HIP68807   &  14\phn05\phn13.0 &  $-$14\phn51\phn25.5 & 7.25 &  0.93 & 03/13/2011 & 23:53 & 5      
\enddata
\tablenotetext{a}{Transformed from SDSS photometry following \citet{Jordi2006}}
\end{deluxetable*}

\begin{figure}
 \begin{center}
  \includegraphics[width=9cm]{Mgspecs_fixed.eps}
  \caption{High-resolution spectrum of our target star, Segue1-11, and the three comparison stars from the F00 sample, in the region around the Mg b-lines. Shown here are the short exposures of the comparison stars, taken to obtain a similar resolution and S/N as the Segue1-11 spectrum.}
  \label{fig:mglines}
 \end{center}
\end{figure}

\subsection{Line Strength Measurements}
\label{sec:linemes}
We obtained a first estimate for the radial velocity from the two strong Mg b lines in the green region of the spectrum, and two additional Mg lines in the blue. Equivalent widths were then measured by fitting Gaussian profiles, and our estimate corrected based on the mean radial velocity from all the lines measured. Using these 366 lines, we find a heliocentric radial velocity of $307.6$~km~s$^{-1}$, with a standard error of the mean of 0.1~km~s$^{-1}$. This is slightly higher than the estimate of $301$~km~s$^{-1}$ from N10 based on the medium resolution spectrum, but consistent within their estimated velocity uncertainty of 10~km~s$^{-1}$. We note that our measurement is well within the estimated range for the 300~km~s$^{-1}$ stream.

@@

For comparison, we also use the SDSS colors to determine the temperature photometrically by interpolating the SDSS {\it ugriz} colors to the isochrones from \citet{Kim2002}, using the color tables of Castelli (http://wwwuser.oat.ts.astro.it/castelli/).  This results in a slightly warmer solution (depending on which colors we use), with T$_{\mbox{\small{eff}}} \sim 5400$ K and $\log g \sim 3.5$. If we instead use this set of stellar parameters, we would arrive at [Fe/H] of $-1.3$. This is, however, well within our estimate of uncertainty for the metallicity (see Section~\ref{sec:unc}). For the rest of the analysis, we use the parameters derived from spectroscopy to facilitate the relative analysis with the \citet{Fulbright2000} stars.

@@

\bibitem[{{Casey} {et~al.}(2012){Casey}, {Keller}, {Da Costa}}]{Casey2012}
{Casey}, A. R., {et~al.} 2012, \aj, 143, 88
